---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}

activity <-read.csv('activity.csv')
aggSteps <- aggregate(steps ~ date, data = activity, sum, na.rm =TRUE)
summary(aggSteps)    
```

## What is mean total number of steps taken per day?
###1. Histogram of total number of steps taken
```{r}
hist(aggSteps$steps)
```

###2. Mean and Median total number of steps take per day
```{r}
mean(aggSteps$steps, na.rm=TRUE)
median(x = aggSteps$steps, na.rm = TRUE)

```
- The mean total is `10766.19` steps per day
- The median total is `10765` steps

## What is the average daily activity pattern?
###1. Time series plot of the 5-minute interval(x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
stepsInterval <- aggregate(steps ~ interval, data = activity, mean, na.rm = TRUE)
plot(steps ~ interval, data = stepsInterval, type = "l")
```

###2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
stepsInterval[which.max(stepsInterval$steps), ]$interval
```

## Inputing missing values

### Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
sum(is.na(activity$steps))
```

### Devise a strategy for filling in all of the missing values in the dataset. 

```{r}
interval2steps <- function(interval) {
    stepsInterval[stepsInterval$interval == interval, ]$steps
}

```

### Create a new dataset
