---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}

activity <-read.csv('activity.csv')
aggSteps <- aggregate(steps ~ date, data = activity, sum, na.rm =TRUE)
summary(aggSteps)    
```

## What is mean total number of steps taken per day?
*1. Histogram of total number of steps taken*
```{r}
hist(aggSteps$steps)
```

*2. Mean and Median total number of steps take per day*
```{r}
mean(aggSteps$steps, na.rm=TRUE)
median(x = aggSteps$steps, na.rm = TRUE)

```
- The mean total is `10766.19` steps per day
- The median total is `10765` steps

## What is the average daily activity pattern?
*1. Time series plot of the 5-minute interval(x-axis) and the average number of steps taken, averaged across all days (y-axis)*
```{r}
stepsIntervalMinutes <- aggregate(steps ~ interval, data = activity, mean, na.rm = TRUE)
plot(steps ~ interval, data = stepsIntervalMinutes, type = "l")
```

*2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?*

```{r}
stepsIntervalMinutes[which.max(stepsIntervalMinutes$steps), ]$interval
```

## Inputing missing values

*1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)*
```{r}
sum(is.na(activity$steps))
```

*2. Devise a strategy for filling in all of the missing values in the dataset.* 

```{r}
intervalSteps <- function(interval) {
    stepsIntervalMinutes[stepsIntervalMinutes$interval == interval, ]$steps
}

```

*3. Create a new dataset*
```{r}
activityFilled <- activity
count = 0
for (i in 1:nrow(activityFilled)) {
    if (is.na(activityFilled[i, ]$steps)) {
        activityFilled[i, ]$steps <- intervalSteps(activityFilled[i, ]$interval)
        count = count + 1
    }
}
cat("Total ", count, "NA values were filled.\n")
```
*4. Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.*

```{r}
totalSteps2 <- aggregate(steps ~ date, data = activityFilled, sum)
hist(totalSteps2$steps)
mean(totalSteps2$steps)
median(totalSteps2$steps)
```

##Are there differences in activity patterns between weekdays and weekends?
*1. Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.*
```{r}
activityFilled$day = ifelse(as.POSIXlt(as.Date(activityFilled$date))$wday%%6 == 
    0, "weekend", "weekday")
# For Sunday and Saturday : weekend, Other days : weekday
activityFilled$day = factor(activityFilled$day, levels = c("weekday", "weekend"))
```
*2. Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). The plot should look something like the following, which was creating using simulated data:*
```{r}
stepsIntervalMinutes2 = aggregate(steps ~ interval + day, activityFilled, mean)
library(lattice)
xyplot(steps ~ interval | factor(day), data = stepsIntervalMinutes2, aspect = 1/2, 
    type = "l")

```